cvx-flats

### 2020-05-18 neurips-20/cvx-flats-statements.tex
I think the def 5 finally makes sense

%\raf{Issues with the definition:
%\begin{enumerate}
%\item Good to clarify $d:\R\times\R\to\reals_+$ -- done
%\item We have two $d$'s so we'll need a new letter... -- changed to $\mu$
%\item $D_X$ is not defined, but I got it -- clarified it was the marginal distribution
%\item You can't take an expectation over $\R$ values (not necessarily a subset of a vector space) and want the expectation over $X$ on the outside
%\end{enumerate}
%At this point I lost the thread. It looks like you're missing the hypothesis function, and $\Gamma(D)$ doesn't seem to type check -- but perhaps $\Gamma(D)$ was meant to depend on $X$ and be the hypothesis? -- and the implication also seems backwards.}
\begin{definition}[Consistent: property]
	Let $\{f_m: \X \to \R\}$ be a sequence of hypothesis functions.
	A loss $L : \R \times \Y \to \reals$ and link $\psi : \R \to \R'$ pair $(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a distance $\mu:\R \times \R \to \reals_+$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and 
	\begin{equation}
	\E_{(X,Y) \sim D} L(\psi \circ f_m(X), Y) \to \E_{(X,Y) \sim D} L( \gamma(D_X), Y) \implies \E_X \mu(\gamma(D_X), \psi \circ f_m(X)) \to 0~.~
	\end{equation}
	If $\mu$ has a set as input, define $\mu(S_1, S_2) = \inf_{s_1 \in S_1, s_2 \in S_2} \mu(s_1, s_2)$.
\end{definition}

@@

\begin{definition}[Calibrated]\label{def:calibrated-general}
	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
	\begin{equation}\label{eq:calibrated-general}
	\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - \risk{L}(p) \right)~.~
	\end{equation}
\end{definition}
\begin{definition}[Calibrated: Finite predictions]\label{def:calibrated-finite}
	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
	A surrogate loss $L : \reals^d \times \Y \to \reals_+$  and link $\psi:\reals^d \to \R$ pair $(L, \psi)$ is \emph{calibrated} with respect to $\ell$ if 
	\begin{equation}\label{eq:calibration}
	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p)~.~
	\end{equation}
\end{definition}

@@

\jessie{Need to redo this}
If we are just given the property $\gamma$ without a loss, assume that we have a sequence of measurable hypotheses $\{f_m\} \to f$ such that $\E_{(X,Y) \sim D} L(\psi \circ f_m(D_X), Y) \to \E_{(X,Y) \sim D} L(\gamma(D_X), Y)$.
We must then have $\E_X \mu(\gamma(D_X), \psi \circ f_m(X)) \to 0$ by consistency.
As in the proof of Proposition~\ref{prop:consistent-implies-calibrated}, this must be true for all $D_x$ for $x \in \X$, so we can abstract to distributions over $\simplex$.
Now, by consistency, we have the expected losses converging implies $\{\psi \circ f_m\}$ is converging toward the optimal hypothesis for all possible inputs $x \in \X$.

Let $\Gamma$ be the property directly elicited by $L$.
We have $\Gamma(D_x) = f(x)$ for all $x \in \X$, so we can see that the precedent being true implies $\mu(\psi \circ f_m(x), \gamma(p)) \to 0$ for all $p\in \simplex$.
As $\mu$ is a distance, $\mu(\psi \circ f(x), \Gamma(p)) = \mu(\psi \circ \Gamma(p), \gamma(p)) = 0$ for all $p \in \simplex$, which implies $\gamma = \psi \circ \Gamma$.
Therefore, $L$ must indirectly elicit the property $\gamma = \lim_{m \to \infty} \{\gamma_m\}$ via the link $\psi$.
\end{proof}

>>>>

%\raf{Issues with the definition:
%\begin{enumerate}
%\item Good to clarify $d:\R\times\R\to\reals_+$ -- done
%\item We have two $d$'s so we'll need a new letter... -- changed to $\mu$
%\item $D_X$ is not defined, but I got it -- clarified it was the marginal distribution
%\item You can't take an expectation over $\R$ values (not necessarily a subset of a vector space) and want the expectation over $X$ on the outside
%\end{enumerate}
%At this point I lost the thread. It looks like you're missing the hypothesis function, and $\Gamma(D)$ doesn't seem to type check -- but perhaps $\Gamma(D)$ was meant to depend on $X$ and be the hypothesis? -- and the implication also seems backwards.}
\begin{definition}[Consistent: property]
	Let $\{f_m: \X \to \R\}$ be a sequence of hypothesis functions.
	Suppose we are given a loss $L : \R \times \Y \to \reals$ and link $\psi : \R \to \R'$.
	$(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a distance $\mu:\R \times \R \to \reals_+$, if for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and 
	\begin{equation}
	\E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \mu(\psi \circ f_m(X), \gamma(D_X)) \to 0~.~
	\end{equation}
	If $\mu$ has a set as input, define $\mu(S_1, S_2) = \inf_{s_1 \in S_1, s_2 \in S_2} \mu(s_1, s_2)$.

	We simply say the pair is consistent with respect to $\gamma$ if there is a distance $\mu$ such that $(L,\psi)$ are $\mu$-consistent with respect to $\gamma$.
\end{definition}

@@

\begin{definition}[Calibrated]\label{def:calibrated-general}
	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a loss $\ell : \R \times \Y \to \reals$ eliciting the property $\gamma$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists a function $\zeta : \reals_+ \to \reals_+$ with $\zeta$ continuous at $0^+$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
	\begin{equation}\label{eq:calibrated-general}
	\ell( \psi(u); p) - \risk{\ell}(p)  \leq \zeta \left(  L(u;p) - \risk{L}(p) \right)~.~
	\end{equation}
\end{definition}
\begin{definition}[Calibrated: Finite predictions]\label{def:calibrated-finite}
	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
	A surrogate loss $L : \reals^d \times \Y \to \reals_+$  and link $\psi:\reals^d \to \R$ pair $(L, \psi)$ is \emph{calibrated} with respect to $\ell$ if 
	\begin{equation}\label{eq:calibration}
	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p)~.~
	\end{equation}
\end{definition}

@@

\jessie{Need to redo this}
If we are just given the property $\gamma$ without a loss eliciting it, assume that we have a sequence of measurable hypotheses $\{f_m\} \to f$ such that $\E_{(X,Y) \sim D} L(\psi \circ f_m(D_X), Y) \to \inf_{f^*}\E_{(X,Y) \sim D} L(f^*(X), Y)$.
We must then have $\E_X \mu(f_m(X), \Gamma(D_X)) \to 0$ by consistency.
As in the proof of Proposition~\ref{prop:consistent-implies-calibrated}, this must be true for all $D$ with a point mass on one $x \in X$, so we can abstract to distributions over $\simplex$.

Fix $p \in \simplex = D_x$ and suppose we have $\{u_m\} \to u$ so that $f_m(x) = u_m$, so $\mu(u_m, \Gamma(p)) \to 0$ by consistency.
As $\mu(x,y) = 0$ if and only if $x$ and $y$ share an element in common (since $\mu$ is a distance), we must have $u \in \Gamma(p)$.
As $\gamma(p) = \{\psi(u) : u \in \Gamma(p)\}$, we then have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$; hence, indirect elicitation.
\jessie{Definitely missing some crucial details.}
%Now, by consistency, we have the expected losses converging implies $\{\psi \circ f_m\}$ is converging toward the optimal hypothesis for all possible inputs $x \in \X$.
%
%Let $\Gamma$ be the property directly elicited by $L$.
%We have $\Gamma(D_x) = f(x)$ for all $x \in \X$, so we can see that the precedent being true implies $\mu(\psi \circ f_m(x), \gamma(p)) \to 0$ for all $p\in \simplex$.
%As $\mu$ is a distance, $\mu(\psi \circ f(x), \Gamma(p)) = \mu(\psi \circ \Gamma(p), \gamma(p)) = 0$ for all $p \in \simplex$, which implies $\gamma = \psi \circ \Gamma$.
%Therefore, $L$ must indirectly elicit the property $\gamma = \lim_{m \to \infty} \{\gamma_m\}$ via the link $\psi$.
\end{proof}
